Appendix part 2

### 2023-05-30 Output/appendix_v4_part2.Rmd
Submission round two updates

---
title: "Appendix part 2"
author: "Cole J. Harvey (Oklahoma State University)"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
    bookdown::pdf_document2: default
linkcolor: blue
bibliography: C:/Users/colej/Documents/Research projects/bib_ch.bib
#biblio-style: "apalike"
fontsize: 12pt
link-citations: yes
toc: false
csl: C:/Users/colej/Documents/Research projects/ji_manipulation_protest/american-journal-of-political-science.csl
header-includes: \usepackage{booktabs}
---
```{r setup, include = FALSE}
library(tidyverse)
library(countrycode)
library(readxl)
library(vdemdata)
library(lme4)
library(interplot)
library(lubridate)
library(summarytools)
library(stargazer)
library(cowplot)
library(pscl)
library(modelsummary)
library(ggeffects)
library(MASS)

nelda_massmob <- read.csv(here::here("Data", "nelda_massmob_all.csv")) #nelda_complete.csv for only elex-related

@@

## Removing cases where inc. loses
nelda_massmob <- nelda_massmob %>% filter(inc.lose == 0)

@@

## Alternative measures of election manipulation

To ensure that the results presented in the main text are not biased by the chosen measure of election fraud, this section replaces that measure with a broader indicator of election integrity from V-Dem. This variable is `v2xel_frefair,' which is a comprehensive indicator of quality of the electoral process, including measures of electoral management body autonomy and capacity, vote-buying, intimidation, fraud, and an overall assessment of the fairness of the election. This variable ranges from 0 to 1, with higher values indicating freer and fairer elections. The models presented below utilize this variable in place of the main measure of election fraud, while retaining all other control and explanatory variables, using the Mass Mobilization data on protest.

```{r manipdv, echo=FALSE}
m1 <- lmer(v2xel_frefair ~ jucon.1lag + legcon.1lag + gdpgro.1lag + altinf.1lag  + osorg.1lag + econ.crisis.nelda.1lag + natlpartyorg.lag   + presidential + inc.termlimit.num  +  libdem.1lag + urban.pct + rentierstate + taxstate + n.events.massmob.pre + median.participants.mm.pre  + (1 | stateid), data = nelda_massmob %>% filter(n.events.massmob.pre < 200)) #There are two extreme observations removed by this filter

@@

modelsummary(m1, stars = T,  title = 'Random-intercept multilevel model of overall election integrity')
```

The first model shows that the number of pre-election protests is weakly associated with improved election integrity, but just as in the main text this effect is extremely small. Each additional protest is associated with an improvement in election integrity equivalent to 0.2\% of the standard deviation of the dependent variable. Given that the mean number of pre-election protests is six, this is an extremely small influence on the overall degree of election integrity.

```{r models-hurdle-mm, warning = FALSE, message = FALSE, include = F}
model.n.novoteshare.hurd.mm <- hurdle(n.events.massmob.post ~ jucon.1lag + legcon.1lag + altinf.1lag + gdpgro.1lag + pubseccorrup.lag + osorg.1lag + econ.crisis.nelda.1lag + natlpartyorg.lag + v2xel_frefair + pubseccorrup.lag +    + v2xel_frefair  + presidential + inc.termlimit.num  +  physinteg.1lag + physintlag.sq + urban.pct + rentierstate + taxstate + n.events.massmob.pre | jucon.1lag + legcon.1lag + gdpgro.1lag + altinf.1lag + pubseccorrup.lag + osorg.1lag + econ.crisis.nelda.1lag + natlpartyorg.lag + v2xel_frefair + pubseccorrup.lag +     + v2xel_frefair  + presidential + inc.termlimit.num  +  physinteg.1lag + physintlag.sq + urban.pct + rentierstate + taxstate + n.events.massmob.pre , data = nelda_massmob %>% filter(gdpgro.1lag < 1), dist = "negbin")
summary(model.n.novoteshare.hurd.mm)

model.n.base.hurd.mm <- hurdle(n.events.massmob.post ~ jucon.1lag + legcon.1lag + altinf.1lag + gdpgro.1lag + pubseccorrup.lag + osorg.1lag + econ.crisis.nelda.1lag + natlpartyorg.lag + v2xel_frefair + pubseccorrup.lag +    winner.share.upd + v2xel_frefair  + presidential + inc.termlimit.num  +  physinteg.1lag + physintlag.sq + urban.pct + rentierstate + taxstate + n.events.massmob.pre | jucon.1lag + legcon.1lag + gdpgro.1lag + altinf.1lag + pubseccorrup.lag + osorg.1lag + econ.crisis.nelda.1lag + natlpartyorg.lag + v2xel_frefair + pubseccorrup.lag +    winner.share.upd + v2xel_frefair  + presidential + inc.termlimit.num  +  physinteg.1lag + physintlag.sq + urban.pct + rentierstate + taxstate + n.events.massmob.pre , data = nelda_massmob %>% filter(gdpgro.1lag < 1), dist = "negbin")
summary(model.n.base.hurd.mm)

model.n.base2.hurd.mm <- hurdle(n.events.massmob.post ~  jucon.1lag + legcon.1lag + gdpgro.1lag + altinf.1lag + pubseccorrup.lag + osorg.1lag + econ.crisis.nelda.1lag + natlpartyorg.lag + v2xel_frefair + pubseccorrup.lag +    winner.share.upd*v2xel_frefair  + presidential + inc.termlimit.num  +  physinteg.1lag + physintlag.sq + urban.pct + rentierstate + taxstate + n.events.massmob.pre |  jucon.1lag + legcon.1lag + gdpgro.1lag + altinf.1lag + pubseccorrup.lag + osorg.1lag + econ.crisis.nelda.1lag + natlpartyorg.lag + v2xel_frefair + pubseccorrup.lag +    winner.share.upd*v2xel_frefair  + presidential + inc.termlimit.num  +  physinteg.1lag + physintlag.sq + urban.pct + rentierstate + taxstate + n.events.massmob.pre, data = nelda_massmob %>% filter(gdpgro.1lag < 1), dist = "negbin")
summary(model.n.base2.hurd.mm)

model.n.griev.hurd.mm <- hurdle(n.events.massmob.post ~ jucon.1lag + legcon.1lag + gdpgro.1lag + altinf.1lag +  osorg.1lag +  natlpartyorg.lag + v2xel_frefair + pubseccorrup.lag +   gdpgro.1lag*v2xel_frefair  + presidential + inc.termlimit.num  +  physinteg.1lag + physintlag.sq + urban.pct + rentierstate + taxstate + n.events.massmob.pre | jucon.1lag + legcon.1lag + gdpgro.1lag + altinf.1lag +  osorg.1lag +  natlpartyorg.lag + v2xel_frefair + pubseccorrup.lag +   gdpgro.1lag*v2xel_frefair  + presidential + inc.termlimit.num  +  physinteg.1lag + physintlag.sq + urban.pct + rentierstate + taxstate + n.events.massmob.pre, dist = "negbin", data = nelda_massmob %>% filter(gdpgro.1lag < 1))
summary(model.n.griev.hurd.mm)

model.n.griev2.hurd.mm <- hurdle(n.events.massmob.post ~ jucon.1lag + legcon.1lag + osorg.1lag + altinf.1lag + econ.crisis.nelda.1lag + natlpartyorg.lag + v2xel_frefair + pubseccorrup.lag +   econ.crisis.nelda.1lag*v2xel_frefair  + presidential + inc.termlimit.num  +  physinteg.1lag + physintlag.sq + urban.pct + rentierstate + taxstate + n.events.massmob.pre | jucon.1lag + legcon.1lag  + altinf.1lag + osorg.1lag + econ.crisis.nelda.1lag + natlpartyorg.lag + v2xel_frefair + pubseccorrup.lag +   econ.crisis.nelda.1lag*v2xel_frefair  + presidential + inc.termlimit.num  +  physinteg.1lag + physintlag.sq + urban.pct + rentierstate + taxstate + n.events.massmob.pre , data = nelda_massmob, dist = "negbin")
summary(model.n.griev2.hurd.mm)

model.n.griev3.hurd.mm <- hurdle(n.events.massmob.post ~ jucon.1lag + legcon.1lag + altinf.1lag +  pubseccorrup.lag + osorg.1lag +  natlpartyorg.lag + v2xel_frefair + pubseccorrup.lag +   pubseccorrup.lag*v2xel_frefair  + presidential + inc.termlimit.num  +  physinteg.1lag + physintlag.sq + urban.pct + rentierstate + taxstate + n.events.massmob.pre  | jucon.1lag + legcon.1lag + altinf.1lag +  pubseccorrup.lag + osorg.1lag +  natlpartyorg.lag + v2xel_frefair + pubseccorrup.lag +   pubseccorrup.lag*v2xel_frefair  + presidential + inc.termlimit.num  +  physinteg.1lag + physintlag.sq + urban.pct + rentierstate + taxstate + n.events.massmob.pre, data = nelda_massmob, dist = "negbin")
summary(model.n.griev3.hurd.mm)
```

Moving to the hurdle models of post-election protest, we do not observe much of a relationship between overall election integrity and protest. There is no statistically significant relationship between election integrity and protest occurrence in Model 2. Neither is there any significant relationship in interaction with the winner's vote-share, as shown in Figure \@ref(fig:b-protests-margin), or with economic crisis, as in Figure \@ref(fig:b-protests-crisis). The coefficient on the interaction term for public sector corruption and overall election integrity is statistically significant, though there is no significant effect at typical values for covariates and election integrity (as shown in Figure \@ref(fig:b-protests-corrupt)).

In the corresponding results for the number of post-election protests, there is similarly muted evidence for a connection between the overall level of manipulation and protest risk to incumbents. There is no significant difference between the marginal effect of common levels of election integrity on the number of post-election protests for typical cases across any margin of victory (Figure \@ref(fig:n-protests-margin)). During an economic crisis, *cleaner* elections are associated with an increase in the number of protests (\@ref(fig:n-protests-crisis)). This is plausibly due to the crisis weakening both the government's ability to generate manipulation [@greene_why_2007] and its ability to co-opt or put down the protests. Finally, public sector corruption is associated with a significant increase in the marginal effect of poor-integrity elections on protest\textemdash but only when the corruption measure is at its maximum (Figure \@ref(fig:n-protests-corrupt)).

As a whole, the results are in accordance with the theory proposed in the main paper. There is no consistent evidence that lower-quality elections are associated with either a higher risk of protest initiation, or with a larger number of post-election protests.

```{r zero-model-table, echo=FALSE}

models <- list()
models[['Model 2']] <- model.n.base.hurd.mm
models[['Model 3']] <- model.n.base2.hurd.mm
#models[['Model 4']] <- model.n.griev.hurd.mm
models[['Model 4']] <- model.n.griev2.hurd.mm
models[['Model 5']] <- model.n.griev3.hurd.mm

modelsummary::modelsummary(models, coef_omit = "count", gof_omit = "R2", stars = T, longtable=T,  title = 'Binary portion of hurdle models of post-election protest')

@@

```{r zero-model-table-count, echo=FALSE}
modelsummary::modelsummary(models, coef_omit = "zero", gof_omit = "R2", longtable=T, stars = T, title = 'Hurdle models of post-election protest (counts)')

@@

```{r, echo=FALSE, message=FALSE}
dat <- ggpredict(model.n.base2.hurd.mm, terms = c("winner.share.upd", "v2xel_frefair [.2, .7]")) 
p.n.margin <- plot(dat)
p.n.margin <- p.n.margin  + theme_bw()

dat <- ggpredict(model.n.base2.hurd.mm, terms = c("winner.share.upd", "v2xel_frefair [.2, .7]"), type = "zi_prob") 
p.b.margin <- plot(dat)
p.b.margin <- p.b.margin  + theme_bw()

@@

```{r n-protests-margin, fig.cap="Fraud, public sector corruption, and number of protest events"}
p.n.margin

@@

```{r b-protests-margin, fig.cap="Fraud, public sector corruption, and likelihood of protest"}
p.b.margin

@@

```{r, echo=FALSE, message=FALSE}
dat <- ggpredict(model.n.griev2.hurd.mm, terms = c("econ.crisis.nelda.1lag", "v2xel_frefair [.15, .66]")) 
p.n.crisis <- plot(dat)
p.n.crisis <- p.n.crisis  + theme_bw()

dat <- ggpredict(model.n.griev2.hurd.mm, terms = c("econ.crisis.nelda.1lag", "v2xel_frefair [.15, .66]"), type = "zi_prob") 
p.b.crisis <- plot(dat)
p.b.crisis <- p.b.crisis +  theme_bw()

```
```{r n-protests-crisis, fig.cap="Fraud, economic crisis, and number of protest events"}
p.n.crisis
```

```{r b-protests-crisis, fig.cap="Fraud, economic crisis, and likelihood of protest"}
p.b.crisis
```

```{r, echo=FALSE, message=FALSE}
dat <- ggpredict(model.n.griev3.hurd.mm, terms = c("pubseccorrup.lag", "v2xel_frefair [.29, .66]")) 
p.corr.n.margin <- plot(dat)
p.corr.n.margin <- p.corr.n.margin + coord_cartesian(ylim = c(0, 100)) + theme_bw()

dat <- ggpredict(model.n.griev3.hurd.mm, terms = c("pubseccorrup.lag", "v2xel_frefair [.29, .66]"), type = "zi_prob") 
p.corr.b.margin <- plot(dat)
p.corr.b.margin <- p.corr.b.margin  + theme_bw()

@@

```{r n-protests-corrupt, fig.cap="Fraud, public sector corruption, and number of protest events"}
p.corr.n.margin
```

```{r b-protests-corrupt, fig.cap="Fraud, public sector corruption, and likelihood of protest"}
p.corr.b.margin
```

>>>>

---
title: "Appendix part 2"
author: "Cole J. Harvey (Oklahoma State University)"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
    bookdown::pdf_document2: default
linkcolor: blue
bibliography: C:/Users/colej/Documents/Research projects/bib_ch.bib
#biblio-style: "apalike"
fontsize: 12pt
link-citations: yes
toc: false
csl: C:/Users/colej/Documents/Research projects/ji_manipulation_protest/american-journal-of-political-science.csl
header-includes: \usepackage{booktabs}
---
```{r setup, include = FALSE}
library(tidyverse)
library(countrycode)
library(readxl)
library(vdemdata)
library(lme4)
library(interplot)
library(lubridate)
library(summarytools)
library(stargazer)
library(ggeffects)
library(glmmTMB)
library(modelsummary)
library(huxtable)
library(simPH)
library(survival)

nelda_massmob <- read.csv(here::here("Data", "nelda_massmob_all.csv")) #nelda_complete.csv for only elex-related
nelda2.sub <- read.csv(here::here("Data", "nelda2_sub_2023-05-22.csv"))

##Bringing nelda2.sub variables over to massmob dataset
nelda2_select <- nelda2.sub %>% dplyr::select(NeldaID, regime_age, v2elirreg.inv.lag)
nelda_massmob <- nelda_massmob %>% rename(NeldaID = electionid)

nelda_massmob <- nelda_massmob %>% left_join(nelda2_select, by = "NeldaID")

@@

## Removing cases where inc. loses
#nelda_massmob <- nelda_massmob %>% filter(inc.lose == 0)

@@

# Robustness check using Mass Mobilization dataset

Not including duration or size data since MassMob data includes all protest, not just election focused and has less reliable size data. Will still use number.

```{r}
m1 <- lmer(v2elirreg.inv ~ jucon.1lag + legcon.1lag + gdpgro.1lag +  osorg.1lag + econ.crisis.nelda.1lag + natlpartyorg.lag   +  presidential + libdem.1lag + urban.pct + rentierstate + taxstate + n.events.massmob.pre +  physinteg.1lag + physintlag.sq    + unscheduled_election + regime_age + (1 | stateid), data = nelda_massmob)

@@

m1b <- lmer(v2elirreg.inv ~ v2elirreg.inv.lag + jucon.1lag + legcon.1lag  + gdpgro.1lag +  osorg.1lag + econ.crisis.nelda.1lag + natlpartyorg.lag   + presidential   +  libdem.1lag + urban.pct + rentierstate + taxstate + n.events.massmob.pre +  physinteg.1lag + physintlag.sq  + unscheduled_election + regime_age+ (1 | stateid), data = nelda_massmob) 
summary(m1b)
```

```{r}
nelda_massmob <- nelda_massmob %>% mutate(n.events.massmob.pre_any = ifelse(n.events.massmob.pre > 0, 1, 0)) #Including the raw value of this variable becomes almost perfectly predictive of the zero-inflation portion of the model

model.n.base2.hurd.mm <- glmmTMB::glmmTMB(n.events.massmob.post ~  jucon.1lag + legcon.1lag + gdpgro.1lag + altinf.1lag + pubseccorrup.lag + osorg.1lag + econ.crisis.nelda.1lag + natlpartyorg.lag + v2elirreg.inv + pubseccorrup.lag +    winner.share.upd*v2elirreg.inv  + presidential + inc.termlimit.num  +  physinteg.1lag + physintlag.sq + urban.pct + rentierstate + taxstate + n.events.massmob.pre + unscheduled_election + regime_age + inc.lose,
                                          zi = ~  jucon.1lag + legcon.1lag + gdpgro.1lag + altinf.1lag + pubseccorrup.lag + osorg.1lag + econ.crisis.nelda.1lag + natlpartyorg.lag + v2elirreg.inv + pubseccorrup.lag +    winner.share.upd*v2elirreg.inv  + presidential + inc.termlimit.num  +  physinteg.1lag + physintlag.sq + urban.pct + rentierstate + taxstate + n.events.massmob.pre_any + unscheduled_election + regime_age + inc.lose,
                                          family= nbinom2,
                                          data = nelda_massmob)
summary(model.n.base2.hurd.mm)

model.n.griev.hurd.mm <- glmmTMB::glmmTMB(n.events.massmob.post ~ jucon.1lag + legcon.1lag + gdpgro.1lag + altinf.1lag +  osorg.1lag +  natlpartyorg.lag + v2elirreg.inv + pubseccorrup.lag +   gdpgro.1lag*v2elirreg.inv  + presidential + inc.termlimit.num  +  physinteg.1lag + physintlag.sq + urban.pct + rentierstate + taxstate + n.events.massmob.pre + unscheduled_election + regime_age+ inc.lose,
                                ziformula=~  jucon.1lag + legcon.1lag + gdpgro.1lag + altinf.1lag + pubseccorrup.lag + osorg.1lag + econ.crisis.nelda.1lag + natlpartyorg.lag + v2elirreg.inv + pubseccorrup.lag +    winner.share.upd*v2elirreg.inv  + presidential + inc.termlimit.num  +  physinteg.1lag + physintlag.sq + urban.pct + rentierstate + taxstate + n.events.massmob.pre_any + unscheduled_election + regime_age + inc.lose,
                                data = nelda_massmob,
                                family=truncated_nbinom2)
summary(model.n.griev.hurd.mm)

@@

```{r zero-model-table, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

models_t1 <- list()
models_t1[['Model 4']] <- model.n.base2.hurd.mm
models_t1[['Model 5']] <- model.n.griev.hurd.mm
#models_t1[['Model 5']] <- m_duration_count
#models_t1[['Model 6']] <- model.d.base2.hurd
#models_t1[['Model 7']] <- model.d.griev.hurd

t1a <- huxreg(models_t1, tidy_args = c("component" = "zi"), borders = 0, number_format = 2, omit_coefs = c("rentierstate1", "taxstate1", "n.events.pre", "unscheduled_election1", "inc.lose1", "v2elirreg.inv:winner.share.upd", "gdpgro.1lag:v2elirreg.inv"), statistics = character(0)) %>% set_caption("Table 3: Zero-inflated models of protest initiation")

theme_compact(t1a, header_rows = TRUE, header_cols = FALSE)

t1b <- huxreg(models_t1, tidy_args = c("component" = "zi"), borders = 0, number_format = 2, omit_coefs = c("(Intercept)", "jucon.1lag" , "legcon.1lag" , "gdpgro.1lag" , "altinf.1lag" , "pubseccorrup.lag" , "osorg.1lag" , "econ.crisis.nelda.1lag1" , "natlpartyorg.lag" , "v2elirreg.inv" , "pubseccorrup.lag"   , "presidential1" , "inc.termlimit.num1"  ,  "physinteg.1lag" , "physintlag.sq" , "urban.pct")) %>% set_caption("Table 3 cont.: Zero-inflated models of protest initiation")

theme_compact(t1b, header_rows = TRUE, header_cols = FALSE)

models_t2 <- list()
models_t2[['Model 4']] <- model.n.base2.hurd.mm
models_t2[['Model 5']] <- model.n.griev.hurd.mm

t2a <- huxreg(models_t2, tidy_args = c("component" = "cond"), borders = 0, number_format = 2, stars = c(`***` = 0.001, `**` = 0.01, `*` = 0.05, `+` = .1), omit_coefs = c("rentierstate1", "taxstate1", "n.events.pre", "unscheduled_election1", "inc.lose1", "v2elirreg.inv:winner.share.upd", "gdpgro.1lag:v2elirreg.inv"), statistics = character(0)) %>% set_caption("Table 4: Negative binomial models of number of protests")

theme_compact(t2a, header_rows = TRUE, header_cols = FALSE)

t2b <- huxreg(models_t2, tidy_args = c("component" = "cond"), borders = 0, number_format = 2, stars = c(`***` = 0.001, `**` = 0.01, `*` = 0.05, `+` = .1), omit_coefs = c("(Intercept)", "jucon.1lag" , "legcon.1lag" , "gdpgro.1lag" , "altinf.1lag" , "pubseccorrup.lag" , "osorg.1lag" , "econ.crisis.nelda.1lag1" , "natlpartyorg.lag" , "v2elirreg.inv" , "pubseccorrup.lag"   , "presidential1" , "inc.termlimit.num1"  ,  "physinteg.1lag" , "physintlag.sq" , "urban.pct")) %>% set_caption("Table 4 cont.: Negative binomial models of number of protests")

theme_compact(t2b, header_rows = TRUE, header_cols = FALSE)

#modelsummary::modelsummary(models, shape = term + estimate + component ~ model, coef_omit = "count", gof_omit = "R2", stars = T, longtable=T,  title = 'Binary portion of hurdle models of post-election protest', coef_rename = 
#               c("zero_(Intercept)" = "Intercept", "zero_jucon.1lag" = "Judical independence (lag)", "zero_legcon.1lag" = "Leg. constraints (lag)", 
#                 "zero_gdpgro.1lag" = "GDP growth rate (lag)", "zero_altinf.1lag" = "Alternative info. (lag)", 
#                 "zero_osorg.1lag" = "Civil soc. openness (lag)", "zero_econ.crisis.nelda.1lag1" = "Economic crisis", 
#                 "zero_natlpartyorg.lag" = "National party organization (lag)", "zero_presidential1" = "Presidential election",
#                 "zero_inc.termlimit.num" = "Incumbent term-limited",  
#                 "zero_urban.pct" = "Urbanization", "zero_rentierstate" = "Rentier state", "zero_taxstate" = "Tax state",
#                 "zero_n.events.pre" = "Number of pre-election protests", "zero_pubseccorrup.lag" = "Public sector corruption (lag)", "zero_v2elirreg.inv" = "Election fraud",
#                 "zero_physinteg.1lag" = "Physical integrity (lag)", "zero_physintlag.sq" = "Physical integrity (lag), squared", "zero_winner.share.upd" = "Incumbent vote-share", "v2elirreg.inv" = "Election fraud", "zero_unscheduled_election" = "Off-schedule election")) # %>%
#  add_header_above(c(" " = 1, "Protest quantity" = 3, "Maximum protest size" = 3))

@@

Figures \@ref(fig:n-protests-margin-max), \@ref(fig:n-protests-crisis-max), and \@ref(fig:n-protests-corrupt-max) illustrate the marginal effects of extreme values for election fraud on the expected number of post-election protests, based on Models 4 - 6 in the main text. They demonstrate that there is no significant relationship between the severity of fraud and the size of post-election protest waves for any of the moderator variables\textemdash incumbent vote-share, economic crisis, or public sector corruption.

```{r, include=FALSE}
model.n.base2.hurd.mm <- hurdle(n.events.massmob.post ~  jucon.1lag + legcon.1lag + gdpgro.1lag + altinf.1lag + pubseccorrup.lag + osorg.1lag + econ.crisis.nelda.1lag + natlpartyorg.lag + v2elirreg.inv + pubseccorrup.lag +    winner.share.upd*v2elirreg.inv  + presidential + inc.termlimit.num  +  physinteg.1lag + physintlag.sq + urban.pct + rentierstate + taxstate + n.events.massmob.pre |  jucon.1lag + legcon.1lag + gdpgro.1lag + altinf.1lag + pubseccorrup.lag + osorg.1lag + econ.crisis.nelda.1lag + natlpartyorg.lag + v2elirreg.inv + pubseccorrup.lag +    winner.share.upd*v2elirreg.inv  + presidential + inc.termlimit.num  +  physinteg.1lag + physintlag.sq + urban.pct + rentierstate + taxstate + n.events.massmob.pre, data = nelda_massmob %>% filter(gdpgro.1lag < 1), dist = "negbin")
summary(model.n.base2.hurd.mm)

model.n.griev.hurd.mm <- hurdle(n.events.massmob.post ~ jucon.1lag + legcon.1lag + gdpgro.1lag + altinf.1lag +  osorg.1lag +  natlpartyorg.lag + v2elirreg.inv + pubseccorrup.lag +   gdpgro.1lag*v2elirreg.inv  + presidential + inc.termlimit.num  +  physinteg.1lag + physintlag.sq + urban.pct + rentierstate + taxstate + n.events.massmob.pre | jucon.1lag + legcon.1lag + gdpgro.1lag + altinf.1lag +  osorg.1lag +  natlpartyorg.lag + v2elirreg.inv + pubseccorrup.lag +   gdpgro.1lag*v2elirreg.inv  + presidential + inc.termlimit.num  +  physinteg.1lag + physintlag.sq + urban.pct + rentierstate + taxstate + n.events.massmob.pre, dist = "negbin", data = nelda_massmob %>% filter(gdpgro.1lag < 1))
summary(model.n.griev.hurd.mm)

model.n.griev2.hurd.mm <- hurdle(n.events.massmob.post ~ jucon.1lag + legcon.1lag + osorg.1lag + altinf.1lag + econ.crisis.nelda.1lag + natlpartyorg.lag + v2elirreg.inv + pubseccorrup.lag +   econ.crisis.nelda.1lag*v2elirreg.inv  + presidential + inc.termlimit.num  +  physinteg.1lag + physintlag.sq + urban.pct + rentierstate + taxstate + n.events.massmob.pre | jucon.1lag + legcon.1lag  + altinf.1lag + osorg.1lag + econ.crisis.nelda.1lag + natlpartyorg.lag + v2elirreg.inv + pubseccorrup.lag +   econ.crisis.nelda.1lag*v2elirreg.inv  + presidential + inc.termlimit.num  +  physinteg.1lag + physintlag.sq + urban.pct + rentierstate + taxstate + n.events.massmob.pre , data = nelda_massmob, dist = "negbin")
summary(model.n.griev2.hurd.mm)

model.n.griev3.hurd.mm <- hurdle(n.events.massmob.post ~ jucon.1lag + legcon.1lag + altinf.1lag +  pubseccorrup.lag + osorg.1lag +  natlpartyorg.lag + v2elirreg.inv + pubseccorrup.lag +   pubseccorrup.lag*v2elirreg.inv  + presidential + inc.termlimit.num  +  physinteg.1lag + physintlag.sq + urban.pct + rentierstate + taxstate + n.events.massmob.pre  | jucon.1lag + legcon.1lag + altinf.1lag +  pubseccorrup.lag + osorg.1lag +  natlpartyorg.lag + v2elirreg.inv + pubseccorrup.lag +   pubseccorrup.lag*v2elirreg.inv  + presidential + inc.termlimit.num  +  physinteg.1lag + physintlag.sq + urban.pct + rentierstate + taxstate + n.events.massmob.pre, data = nelda_massmob, dist = "negbin")
summary(model.n.griev3.hurd.mm)
```

```{r n-protests-margin-max, fig.cap="Fraud, incumbent vote-share, and number of protest events", echo=FALSE, message=FALSE, out.width = '70%', fig.align='center'}
dat <- ggpredict(model.n.base2.hurd.mm, terms = c("winner.share.upd", "v2elirreg.inv [-2.3, 3.2]")) 
p.n.margin <- plot(dat)
p.n.margin + coord_cartesian(ylim = c(0, 70)) + labs(x = "Incumbent vote-share", y = "Number of events", title = "Predicted counts of protest events", color = "Election fraud") + theme_bw()

@@

```{r n-protests-crisis-max, fig.cap="Fraud, economic crisis, and number of protest events", echo=FALSE, message=FALSE, out.width = '70%', fig.align='center'}
dat <- ggpredict(model.n.griev2.hurd.mm, terms = c("econ.crisis.nelda.1lag", "v2elirreg.inv [-2.3, 3.2]")) 
p.n.crisis <- plot(dat)
p.n.crisis + coord_cartesian(ylim = c(0, 125)) + labs(x = "Economic crisis", y = "Number of events", title = "Predicted counts of protest events", color = "Election fraud") + theme_bw()

@@

```{r n-protests-corrupt-max, fig.cap="Fraud, public sector corruption, and number of protest events", echo=FALSE, message=FALSE, out.width = '70%', fig.align='center'}
dat <- ggpredict(model.n.griev3.hurd.mm, terms = c("pubseccorrup.lag", "v2elirreg.inv [-2.3, 3.2]")) 
p.corr.n.margin <- plot(dat)
p.corr.n.margin + coord_cartesian(ylim = c(0, 120)) + labs(x = "Public sector corruption", y = "Number of events", title = "Predicted counts of protest events", color = "Election fraud") + theme_bw()

@@

\newpage

# Removing controls to address multicollinearity

The models in the main text include a suite of control variables aimed at controlling for common causes of election manipulation and protest, in order to minimize the risks of confounding and omitted variable bias. However, this approach runs the risk that individual coefficients may be highly sensitive to model specification due to multicollinearity. In particular, many of the control variables\textemdash such as *legislative constraints*, *judicial independence*, and *physical integrity* are likely to be correlated with pre-election protest. To address this risk, the models in Tables \@ref(tab:zero-model-table-small) and \@ref(tab:zero-model-table-count-small) exclude non-electoral control variables. That is, they include variables related to the election itself, the measure of *pre-election protest*, and the explanatory variables from the main models.

The results echo those from the main text. Severity of election fraud is not associated with an increased number of protests, conditional on incumbent vote-share, economic crisis, or public-sector corruption. Marginal effects for interaction terms are presented in the following figures.

```{r models-hurdlesmall-mm, warning = FALSE, message = FALSE, include = F}
model.small.novoteshare.hurd.mm <- hurdle(n.events.massmob.post ~ v2elirreg.inv + presidential + inc.termlimit.num  + n.events.massmob.pre + unscheduled_election |  v2elirreg.inv + presidential + inc.termlimit.num  + n.events.massmob.pre + unscheduled_election , data = nelda_massmob %>% filter(gdpgro.1lag < 1), dist = "negbin")
summary(model.small.novoteshare.hurd.mm)

model.small.base.hurd.mm <- hurdle(n.events.massmob.post ~  v2elirreg.inv + presidential + inc.termlimit.num  + n.events.massmob.pre + unscheduled_election + winner.share.upd |  v2elirreg.inv + presidential + inc.termlimit.num  + n.events.massmob.pre + unscheduled_election + winner.share.upd , data = nelda_massmob %>% filter(gdpgro.1lag < 1), dist = "negbin")
summary(model.small.base.hurd.mm)

model.small.base2.hurd.mm <- hurdle(n.events.massmob.post ~  v2elirreg.inv + presidential + inc.termlimit.num  + n.events.massmob.pre + unscheduled_election + winner.share.upd + winner.share.upd*v2elirreg.inv | v2elirreg.inv + presidential + inc.termlimit.num  + n.events.massmob.pre + unscheduled_election + winner.share.upd  + winner.share.upd*v2elirreg.inv, data = nelda_massmob %>% filter(gdpgro.1lag < 1), dist = "negbin")
summary(model.small.base2.hurd.mm)

model.small.griev2.hurd.mm <- hurdle(n.events.massmob.post ~  v2elirreg.inv + presidential + inc.termlimit.num  + n.events.massmob.pre + unscheduled_election + winner.share.upd + econ.crisis.nelda.1lag*v2elirreg.inv | v2elirreg.inv + presidential + inc.termlimit.num  + n.events.massmob.pre + unscheduled_election + winner.share.upd + econ.crisis.nelda.1lag*v2elirreg.inv , data = nelda_massmob, dist = "negbin")
summary(model.small.griev2.hurd.mm)

model.small.griev3.hurd.mm <- hurdle(n.events.massmob.post ~ v2elirreg.inv + presidential + inc.termlimit.num  + n.events.massmob.pre + unscheduled_election + winner.share.upd + pubseccorrup.lag*v2elirreg.inv   |   v2elirreg.inv + presidential + inc.termlimit.num  + n.events.massmob.pre + unscheduled_election + winner.share.upd + pubseccorrup.lag*v2elirreg.inv , data = nelda_massmob, dist = "negbin")
summary(model.small.griev3.hurd.mm)
```
\newpage

```{r zero-model-table-small, echo=FALSE}

models <- list()
models[['Model 11']] <- model.small.base.hurd.mm
models[['Model 12']] <- model.small.base2.hurd.mm
#models[['Model ']] <- model.n.griev.hurd.mm
models[['Model 13']] <- model.small.griev2.hurd.mm
models[['Model 14']] <- model.small.griev3.hurd.mm

modelsummary::modelsummary(models, coef_omit = "count", gof_omit = "R2", stars = T, longtable=T,  title = 'Binary portion of hurdle models of post-election protest', coef_rename = 
               c("zero_(Intercept)" = "Intercept", "zero_presidential1" = "Presidential election",
                 "zero_inc.termlimit.num" = "Incumbent term-limited",  
                                  "zero_n.events.massmob.pre" = "Number of pre-election protests", "zero_pubseccorrup.lag" = "Public sector corruption (lag)", "zero_v2elirreg.inv" = "Election fraud", "zero_unscheduled_election" = "Off-schedule election", "zero_winner.share.upd" = "Incumbent vote-share", "v2elirreg.inv" = "Election fraud", "winner.share.upd" = "Incumbent vote-share",
                 "zero_econ.crisis.nelda.1lag1" = "Economic crisis", "econ.crisis.nelda.1lag1" = "Economic crisis",
                 "pubseccorrup.lag" = "Public sector corruption"))

@@

\newpage

```{r zero-model-table-count-small, echo=FALSE}
modelsummary::modelsummary(models, coef_omit = "zero", gof_omit = "R2", longtable=T, stars = T, title = 'Hurdle models of post-election protest (counts)',
                           coef_rename = 
              c("count_(Intercept)" = "Intercept", "count_presidential1" = "Presidential election",
                 "count_inc.termlimit.num" = "Incumbent term-limited",  
                                  "count_n.events.massmob.pre" = "Number of pre-election protests", "count_pubseccorrup.lag" = "Public sector corruption (lag)", "count_v2elirreg.inv" = "Election fraud", "count_unscheduled_election" = "Off-schedule election", "count_winner.share.upd" = "Incumbent vote-share", "v2elirreg.inv" = "Election fraud", "winner.share.upd" = "Incumbent vote-share",
                 "count_econ.crisis.nelda.1lag1" = "Economic crisis", "econ.crisis.nelda.1lag1" = "Economic crisis",
                 "pubseccorrup.lag" = "Public sector corruption"))

```{r, echo=FALSE, message=FALSE, warning=FALSE}
dat <- ggpredict(model.small.base2.hurd.mm, terms = c("winner.share.upd", "v2elirreg.inv [-.44, 1.77]")) 
p.n.margin <- plot(dat)
p.n.margin <- p.n.margin + labs(x = "Incumbent vote-share", y = "Predicted number of protests" , title = "Predicted count of protest events") + coord_cartesian(ylim = c(0, 100)) + theme_bw()
